Women and Highly Educated Toronto Residents Most Likely to Be Concerned About Local Impacts of Climate Change

### 2021-04-27 outputs/paper/paper.Rmd
Title update

---
title: "Women and Highly Educated Toronto Residents Most Concerned About Local Impacts of Climate Change"
author: "Lorena Almaraz De La Garza"
date: "April 26th, 2021"
output:
  bookdown::pdf_document2: default
  fig_caption: yes
subtitle: "A study on climate change perceptions with the City of Toronto's Open Data"
toc: TRUE
thanks: 'Code and data are available in this GitHub repository: [lalmaraz/toronto_climate_perceptions](https://github.com/lalmaraz/toronto_climate_perceptions).'
bibliography: references.bib
abstract: "This report presents a secondary analysis of the City of Toronto's data on residents' perceptions about climate change. The results indicate that respondents' gender, education, and income, affect their self-reported level of concern, and level of information, about climate change. The analysis consists of logistic regression performed with the statistical programming language R. The results contribute to our understanding of the issue at a local level, enabling effective action to address the ongoing threat of climate change.
 \\par
 \\textbf {Keywords:} climate change, climate perceptions, climate concerns, climate action, age and climate, gender and climate, toronto residents, open data toronto"

>>>>

---
title: "Women and Highly Educated Toronto Residents Most Likely to Be Concerned About Local Impacts of Climate Change"
author: "Lorena Almaraz De La Garza"
date: "April 26th, 2021"
output:
  bookdown::pdf_document2: default
  fig_caption: yes
subtitle: "A study on climate change perceptions with the City of Toronto's Open Data"
toc: TRUE
thanks: 'Code and data are available in this GitHub repository: [lalmaraz/toronto_climate_perceptions](https://github.com/lalmaraz/toronto_climate_perceptions).'
bibliography: references.bib
abstract: "This report presents a secondary analysis of the City of Toronto's data on residents' perceptions about climate change. The results indicate that respondents' gender, education, and income, affect their self-reported level of concern, and level of information, about climate change. The analysis consists of logistic regression performed with the statistical programming language R. The results contribute to our understanding of the issue at a local level, enabling effective action to address the ongoing threat of climate change.
 \\par
 \\textbf {Keywords:} climate change, climate perceptions, climate concerns, climate action, age and climate, gender and climate, toronto residents, open data toronto"
